---
title: "Model selection LRT green"
author: "Olsson et al."
date: "1/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages required to run the analysis and the plotting.

```{r}
library('lattice')
library('graphics')
library('psyphy')
library('lmerTest')
library('MASS')
library('glm2')
library('readr')
```

## Reading in the data.
The script is constructed such that you should have one column with the number of correct choices ("corr" in the current version), second column with the number of incorrect choices("incorr" in the current version), and a third column representing the stimulus levels ("lint" in the current version; could be intensity, or whatever). Additional variables can be added.

```{r}
green.df <- read_delim('green_colours.txt', delim = "\t") 
green.df$background <- factor(green.df$background)
green.df$ind <- factor(green.df$ind)
green.df$batch <- as.factor(green.df$batch)
```

## Model testing, full and removing one factor at a time, simulating stepAIC

### setting up models

Null model, data is explained only by variance. lambda.init is your estimate of the upper asymptote and NumAlt specifies the number of alternatives e.g. 2 alternative forced choice.

```{r}
green.m0 <- glm.WH(cbind(corr,incorr)~1, data = green.df, lambda.init = 0.1, interval = c(0, 1), NumAlt = 2) 
```

Model where data is affected by the stimulus level.

```{r message=FALSE, warning=FALSE}
green.m1 <- glm.WH(cbind(corr,incorr)~Colour.difference*background*sex+ind+batch, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, 
                tol=1e-06, maxit=10^2) 
```

Model where data is affected by the stimulus level.

```{r}
green.m2 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+sex+ind+batch, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, 
                 tol=1e-06, maxit=10^2)  
```

Model where data is affected by the stimulus level.

```{r}
green.m21 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+Colour.difference*sex+background*sex+ind+batch, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, 
                 tol=1e-06, maxit=10^2) 
```

Model where data is affected by the stimulus level.

```{r}
green.m3 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+ind+batch, data = green.df, lambda.init = 0.06, interval = c(0, 1), NumAlt = 2, 
                 tol=1e-06, maxit=10^2) 
```

Model where data is affected by the stimulus level.

```{r}
green.m4 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+ind+sex, data = green.df, lambda.init = 0.06, interval = c(0, 1), NumAlt = 2, 
                 tol=1e-06, maxit=10^2) 
```


```{r}
green.m5 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+ind+batch+sex, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, 
                 tol=1e-06, maxit=10^2)  # Model where green.df is affected by the stimulus level
```


```{r}
AIC(green.m0, green.m1, green.m2, green.m3, green.m4, green.m5)
```


```{r}
anova(green.m0, green.m1, test="Chisq")
```


```{r}
anova(green.m1, green.m2, test= "Chisq")
```


```{r}
anova(green.m1, green.m3, test= "Chisq")
```


```{r}
anova(green.m1, green.m4, test= "Chisq")
```



```{r}
anova(green.m1, green.m5, test="Chisq")
```


```{r}
anova(green.m1,green.m2,green.m3,green.m4,green.m5, test="Chisq")
```


```{r}
anova(green.m1)
```


```{r}
summary(green.m1)
```
