---
title: "Model selection LRT green"
author: "Olsson et al."
date: "12/11/2020"
output: html_document
self_contained: no
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages required to run the analysis and the plotting.

```{r message=FALSE, warning=FALSE}
library('lattice')
library('graphics')
library('psyphy')
library('MASS')
library('glm2')
library('readr')
```

## Check system and R version

```{r}
R.version.string
```

## Set up functions for checking model rank deficiency
```{r}
#Green colour
CheckRank <- function(mod){
  cf <- coef(mod)
  if(length(cf)>mod$rank){
    cbind(names(cf)[is.na(cf)])
  }else{'FULL RANK'}
}#a function to check if models are rank deficient and return missing coef

NumCoef <- function(mod, coef = 'ind'){
  cf <- coef(mod)#coefficients
  fit <- c(names(cf[!is.na(cf)]))#which ones did fit
  return(length(grep(coef, fit)))#how many are there
}
```

## Reading in the data

The script is constructed such that you should have one column with the number of correct choices ("corr" in the current version), second column with the number of incorrect choices("incorr" in the current version).

```{r}
green.df <- read.csv('green colours.csv')
green.df$background <- factor(green.df$background)
green.df$ind <- factor(green.df$ind)
green.df$batch <- as.factor(green.df$batch)
```

## Model testing, full and removing one factor at a time

### setting up models

Null model, data is explained only by variance. lambda.init is your estimate of the upper asymptote and NumAlt specifies the number of alternatives e.g. 2 alternative forced choice.


Green colours

###Model testing, null model and full model, and models removing one factor
```{r}
green.mod.0 <- glm.WH(cbind(corr,incorr)~1, data = green.df, lambda.init = 0.1, interval = c(0, 1), NumAlt = 2) # Null model, data is explained only by variance. lambda.init is your estimate of the upper asymptote and NumAlt specifies the number of alternatives e.g. 2 alternative forced choice
CheckRank(green.mod.0)
NumCoef(green.mod.0) 
```
###full model with 3-way interaction
```{r include=F}
green.mod.1 <- glm.WH(cbind(corr,incorr)~Colour.difference*background*sex+ind+batch, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```
###compare null and full model
```{r}
CheckRank(green.mod.1)# Model is rank deficient
anova(green.mod.0,green.mod.1,test="Chisq")
AIC(green.mod.0,green.mod.1)
```

###after removing 3-way interaction
```{r include=F}
green.mod.2 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+Colour.difference*sex+background*sex+ind+batch, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

###comparison with previous preferred model
```{r}
CheckRank(green.mod.2)# Model is rank deficient
anova(green.mod.1,green.mod.2,test="Chisq")
AIC(green.mod.1,green.mod.2)
```

###removing interaction  background:sex
```{r include=F}
green.mod.31 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+Colour.difference*sex+ind+batch, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```

###comparison with previous preferred model
```{r}
CheckRank(green.mod.31)# Model is rank deficient
anova(green.mod.2,green.mod.31,test="Chisq")
AIC(green.mod.31,green.mod.2)
```

###removing interaction colour difference:background
```{r include=F}
green.mod.4 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+Colour.difference*sex+ind+batch, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.4)#Model is rank deficient
anova(green.mod.4,green.mod.31,test="Chisq")
AIC(green.mod.4,green.mod.31)
```

###removing interaction colour difference:sex
```{r include = F}
green.mod.51 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+sex+ind+batch, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.51)#Model is rank deficient
anova(green.mod.51,green.mod.4,test="Chisq")
AIC(green.mod.51,green.mod.4)
```

###removing batch
```{r include = F}
green.mod.61 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+sex+ind, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.61)#Model is rank deficient
anova(green.mod.61,green.mod.51,test="Chisq")
AIC(green.mod.61,green.mod.51)
```

###removing ind
```{r include = F}
green.mod.71 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+sex, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.71)#Model is rank deficient
anova(green.mod.71,green.mod.61,test="Chisq")
AIC(green.mod.71,green.mod.61)
```

###removing sex
```{r include = F}
green.mod.72 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+ind, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.72)#Model is rank deficient
anova(green.mod.72,green.mod.61,test="Chisq")
AIC(green.mod.72,green.mod.61)
```

###removing background
```{r include = F}
green.mod.81 <- glm.WH(cbind(corr,incorr)~Colour.difference+ind, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.81)#Model is *full rank*
anova(green.mod.81,green.mod.72,test="Chisq")
AIC(green.mod.81,green.mod.72)
```

###removing ind
```{r include = F}
green.mod.91 <- glm.WH(cbind(corr,incorr)~Colour.difference, data = green.df, lambda.init = 0.1, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.91)#Model is *full rank*
anova(green.mod.91,green.mod.81,test="Chisq")
AIC(green.mod.91,green.mod.81)
```

###removing colour diff
```{r include = F}
green.mod.92 <- glm.WH(cbind(corr,incorr)~ind, data = green.df, lambda.init = 0.1, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.92)#Model is *full rank*
anova(green.mod.92,green.mod.81,test="Chisq")
AIC(green.mod.92,green.mod.81)
```
#Final model
```{r}
summary(green.mod.81)
```

#Forward Selection
###Adding background
```{r include = F}
green.mod.101 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+ind, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit = 100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.101)#Model is rank deficient
anova(green.mod.101,green.mod.81,test="Chisq")
AIC(green.mod.101,green.mod.81)
```
###adding sex
```{r include = F}
green.mod.102 <- glm.WH(cbind(corr,incorr)~Colour.difference+sex+ind, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit = 100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.102)#Model is rank deficient
anova(green.mod.102,green.mod.81,test="Chisq")
AIC(green.mod.102,green.mod.81)
```
###adding batch
```{r include = F}
green.mod.103 <- glm.WH(cbind(corr,incorr)~Colour.difference+batch+ind, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit = 100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.103)#Model is rank deficient
anova(green.mod.103,green.mod.81,test="Chisq")
AIC(green.mod.103,green.mod.81)
```
###adding colour.difference:sex
```{r include = F}
green.mod.104 <- glm.WH(cbind(corr,incorr)~Colour.difference+ind+Colour.difference:sex, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit = 100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.104)#Model is *full rank*
anova(green.mod.104,green.mod.81,test="Chisq")
AIC(green.mod.104,green.mod.81)
```

###adding background:colour difference #convegence fails
```{r include = F}
green.mod.105 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+ind+Colour.difference:background, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit = 10) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.105)#Model is rank deficient
anova(green.mod.105,green.mod.81,test="Chisq")
AIC(green.mod.105,green.mod.81)
```

###adding background:sex
```{r include = F}
green.mod.106 <- glm.WH(cbind(corr,incorr)~Colour.difference+ind+background:sex, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit = 100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.106)#Model is rank deficient
anova(green.mod.106,green.mod.81,test="Chisq")
AIC(green.mod.106,green.mod.81)
```
###adding colour.diff:background:sex #convegence fails
```{r include = F}
green.mod.107 <- glm.WH(cbind(corr,incorr)~Colour.difference+ind+Colour.difference:background:sex, data = green.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit = 10) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(green.mod.107)#Model is rank deficient
anova(green.mod.107,green.mod.81,test="Chisq")
AIC(green.mod.107,green.mod.81)
```

```{r}
sessionInfo()
```

