---
title: "Model selection LRT orange"
author: "Olsson et al."
date: "12/11/2020"
output: html_document
self_contained: no
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages required to run the analysis and the plotting.

```{r message=FALSE, warning=FALSE}
library('lattice')
library('graphics')
library('psyphy')
library('MASS')
library('glm2')
library('readr')
```

## Check system and R version

```{r}
R.version.string
```
## Set up functions for checking model rank deficiency

```{r}
#orange colour
CheckRank <- function(mod){
  cf <- coef(mod)
  if(length(cf)>mod$rank){
    cbind(names(cf)[is.na(cf)])
  }else{'FULL RANK'}
}#a function to check if models are rank deficient and return missing coef

NumCoef <- function(mod, coef = 'ind'){
  cf <- coef(mod)#coefficients
  fit <- c(names(cf[!is.na(cf)]))#which ones did fit
  return(length(grep(coef, fit)))#how many are there
}
```

## Reading in the data

The script is constructed such that you should have one column with the number of correct choices ("corr" in the current version), second column with the number of incorrect choices("incorr" in the current version).

```{r}
orange.df <- read.csv('orange colours.csv')
orange.df$background <- factor(orange.df$background)
orange.df$ind <- factor(orange.df$ind)
orange.df$batch <- as.factor(orange.df$batch)
```

## Model testing, full and removing one factor at a time

## setting up models

Null model, data is explained only by variance. lambda.init is your estimate of the upper asymptote and NumAlt specifies the number of alternatives e.g. 2 alternative forced choice.

## Model testing, null model and full model, and models removing one factor
```{r}
orange.mod.0 <- glm.WH(cbind(corr,incorr)~1, data = orange.df, lambda.init = 0.1, interval = c(0, 1), NumAlt = 2)
# Null model, data is explained only by variance. lambda.init is your estimate of the upper asymptote and NumAlt specifies the number of alternatives e.g. 2 alternative forced choice
CheckRank(orange.mod.0)
NumCoef(orange.mod.0) 
```

### full model with 3-way interaction
```{r include=F}
orange.mod.1 <- glm.WH(cbind(corr,incorr)~Colour.difference*background*sex+ind+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```
### compare null and full model
```{r}
CheckRank(orange.mod.1)# Model is rank deficient
anova(orange.mod.0,orange.mod.1,test="Chisq")
AIC(orange.mod.0,orange.mod.1)
```
### after removing 3-way interaction
```{r include=F}
orange.mod.2 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+Colour.difference*sex+background*sex+ind+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

### comparison with previous preferred model
```{r}
CheckRank(orange.mod.2)# Model is rank deficient
anova(orange.mod.1,orange.mod.2,test="Chisq")
AIC(orange.mod.1,orange.mod.2)
```
### removing background:sex
```{r include=F}
orange.mod.21 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+Colour.difference*sex+ind+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

### comparison with previous preferred model
```{r}
CheckRank(orange.mod.21)
anova(orange.mod.2,orange.mod.21,test="Chisq")
AIC(orange.mod.2,orange.mod.21)
```
### Removing colour.difference:sex
```{r include=F}
orange.mod.22 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+sex+ind+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(orange.mod.22)
anova(orange.mod.2,orange.mod.22,test="Chisq")
AIC(orange.mod.2,orange.mod.22)
```
### removing colour.difference:background
```{r include=F}
orange.mod.23 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+sex+ind+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(orange.mod.23)
anova(orange.mod.22,orange.mod.23,test="Chisq")
AIC(orange.mod.22,orange.mod.23)
```
### removing batch
```{r include=F}
orange.mod.3 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+sex+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(orange.mod.3)
anova(orange.mod.22,orange.mod.3,test="Chisq")
AIC(orange.mod.22,orange.mod.3)
```
### removing sex
```{r include=F}
orange.mod.31 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(orange.mod.31)
anova(orange.mod.3,orange.mod.31,test="Chisq")
AIC(orange.mod.3,orange.mod.31)
```
### Removing ind
```{r include=F}
orange.mod.4 <- glm.WH(cbind(corr,incorr)~Colour.difference*background, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(orange.mod.4)
anova(orange.mod.31,orange.mod.4,test="Chisq")
AIC(orange.mod.31,orange.mod.4)
```
### removing colour.difference:background interaction
```{r include=F}
orange.mod.5 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(orange.mod.5)
anova(orange.mod.31,orange.mod.5,test="Chisq")
AIC(orange.mod.31,orange.mod.5)
summary(orange.mod.31)
```
## Forward Selection below

### Adding Colour.difference:sex
```{r include=F}
orange.mod.31a <- glm.WH(cbind(corr,incorr)~Colour.difference*background+ind+Colour.difference:sex, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(orange.mod.31a)
anova(orange.mod.31a,orange.mod.31,test="Chisq")
AIC(orange.mod.31,orange.mod.31a)
```
### Adding background:sex
```{r}
orange.mod.31b <- glm.WH(cbind(corr,incorr)~Colour.difference*background+ind+background:sex, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
CheckRank(orange.mod.31b)
anova(orange.mod.31b,orange.mod.31,test="Chisq")
AIC(orange.mod.31,orange.mod.31b)
```

### Adding colour.difference:background:sex
This model did not converge. 
```{r eval=FALSE}
orange.mod.31d <- glm.WH(cbind(corr,incorr)~Colour.difference*background*sex+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

```{r}
sessionInfo()
```

