---
title: "Bayesian Psychometric"
author: "Olsson et al."
date: "11/1/2019"
output: html_document
self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The model object used in these analyses is stored in 'results/Psychometric_Bayesian_model_object.rds'. To use it, load it into an object named: 'Bayes.fit'.

```{r}
library('readr')
library('tidyr')
library('magrittr')
library('rstan')
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
library('brms')
```


```{r}
cd.long <- read_delim('colour_discriminate_long_format.txt', delim="\t")
```

Success in each trial is either TRUE or FALSE. 

```{r}
summary(cd.long)
```


Individual chicken is a factor. We added "chick", which accounts for the fact that "ind" names shared across experiments actually belong to different chicks ("A1" is like "Svensson" in the world of chicks).

```{r}
cd.long$chick  <- as.factor(cd.long$chick)#chick is also a factor
```

We add a row that states whether target was the same or different colour type as the background (e.g. green on green = 'same'). Different is the default reference level

```{r}
cd.long$target <- ifelse(cd.long$target.same, 'same', 'diff')
cd.long$target <- as.factor(cd.long$target)#this is a factor
levels(cd.long$target)
```

We relevel this to be same instead.

```{r}
cd.long$target <- relevel(cd.long$target,'same')
```


Set reference conditions - set same as the reference level. Keep background_green as reference level.

```{r}
cd.long$background <- as.factor(cd.long$background)
levels(cd.long$background)
```

We also split conditions into two factors with an interaction: Backgrounds could be green or orange, and targets could be the same colour type as their background, or a different one.


#	Fit a Non-linear Model with All Fixed Effects		

Formulae and factors are arranged so that reference condition is: background_green & target_same (green on green). This is determined by both the reference levels in the data frame. The order of "background" and "target" in the formula determines naming
 and which one's independent effects are estimated first, i.e. background*target: 1st background, 2nd target, 3rd background:target. With broad unbiased priors this effect is negligible.

Threshold and width are estimated on a log scale, which keeps them positive and allows free reign for random effects lapse is estimated on a logit scale, also allowing free estimation of random effects in [0,1] space.

Mmodel 1, intercept is background_green, target_same:

```{r}
modnm1 <- 'TW.Model-bg_target_REVISION'#distinguish it from others
frm1 <-              bf(
	formula = success ~ base	 +	#guess rate
						(1-inv_logit(lapse)-base) 	* #curve region
			inv_logit(4.39*(	Colour.difference-exp(threshold)	) 	/
						(	exp(width)	)), #threshold-width curve
	  base ~ 1, #baseline has a single mean
	  lapse ~ 1 + (1|chick) +(1|batch),  #lapse rate depends on chick
	  #threshold coef depend on fixef & chick
	 threshold ~ background*target*sex +(1|chick) +(1|batch),
	 #width coef depend on fixef & chick
	 width ~ background*target*sex +(1|chick) +(1|batch),
      nl = TRUE)#the joint distribution for these parameters is undefined, and therefore the parameters themselves are "nonlinear"
```




###	Select Some Priors												

###	Model 1, Raneff of lapse; Intercept:target_green&background_green	

We print the priors.

```{r}
get_prior(frm1, data = cd.long)[,c('class', 'coef','nlpar', 'group')]
```

Only base has a very informative prior.

```{r}
prr1 <- c(
  #very restrictive prior for guess rate, centred on 0.5
	prior(beta(250,250), nlpar= 'base', lb = 0.25, ub = 0.75),
  #lapse rate is unbiased, but cannot be more than 27%
	prior(normal(-3,10), nlpar= 'lapse', ub = -1),
  # use the default prior for random effects of lapse:
  #	student_t(3, 0, 10)),
  # this can be done by leaving:
  #	prior(... nlpar= 'lapse', class= sd), unassigned
  #Both threshold and width should be positive numbers, probably ≈1
  #i.e. exp(0) = 1
  #beware, bounds on threshold and width priors
  #affect their coefficients (so don't apply bounds)
	prior(normal(0,10), nlpar= 'threshold', class = 'b'),
	prior(normal(0,10), nlpar = 'width', class = 'b'),
  #Coefficient parameters, centred on 0
  #(<0 = param smaller, >0 = param larger)
	prior(normal(0,10), nlpar= 'threshold', coef= 'backgroundorange'),
	prior(normal(0,10), nlpar= 'threshold', coef= 'targetdiff'),
	prior(normal(0,10), nlpar= 'threshold', coef= 'backgroundorange:targetdiff'),
  # use the default prior for random effects of threshold, unassigned
	prior(normal(0,10), nlpar= 'width', coef= 'backgroundorange'),
	prior(normal(0,10), nlpar= 'width', coef= 'targetdiff'),
	prior(normal(0,10), nlpar= 'width', coef= 'backgroundorange:targetdiff')#,
  # use the default prior for random effects of width, unassigned
)
```


##	Inspect Stan Code	

```{r}
stc1 <- make_stancode( 
			 formula = frm1,
 	         data = cd.long, family = bernoulli("identity"), 
             prior = prr1 )
stc1
```

### Posterior predictive checks

Check that the priors are valid. This samples from the priors only (and not the data) - the distribution of estimates indicates the range of possible values the model can take and where it is weighted (biased). 

```{r}
Prior.fit <- brm( formula = frm1,
 	           data = cd.long, family = bernoulli("identity"), 
             prior = prr1,
        		 control = list(adapt_delta = 0.9999),
             sample_prior = "only",
        		 inits = 0,
        		 iter = 1000  )
```

We can visualize the range of plausible models using conditional effects.

```{r}
Prior.cond <- conditional_effects(Prior.fit, spaghetti = TRUE, effects = "Colour.difference")
plot(Prior.cond)
```

The plot above shows the model fit at every iteration when using only the priors and not the data. Many values are possible, including many different slopes for the line, though there is definite concentration at certain values. 

###	Run the Model	

200 or 2000 iterations give similar results to 10000. Random effects of threshold and width should change together (ideally, explicit correllation). and setting initial values to 0 is a work-around.

```{r}
Bayes.fit <- brm( formula = frm1,
 	           data = cd.long, family = bernoulli("identity"), 
             prior = prr1,
             #finely sampled
        		control = list(adapt_delta = 0.99),
        		inits = 0,
        		iter = 1000  )
```
 
### Inspect the model

```{r}
plot(Bayes.fit,type="dens_overlay", pars = "^b_")
```


Derive summary information. 

```{r}
summary(Bayes.fit)
```

The ESS and Rhat values confirm that the model converged well. Divergent transitions indicate that a between MC draws an unexpected transition has occurred. 

```{r}
conditional_effects(Bayes.fit)
```

Conditional effects at the mean is used to investigate certain parameters at the mean values of the remaining parameters. 

## Posterior predictive checks (PPCs)

```{r}
pp_check(Bayes.fit,
         type = "rootogram", nsamples=2000, prob = 0.9, size = 1)
```


```{r}
pp_check(Bayes.fit,
         type = "bars", nsamples=200, prob = 0.9, size = 1)
```


These checks show that the predctions are consistent with the observed data.


