---
title: "Model selection LRT orange"
author: "Olsson et al."
date: "07/11/2020"
output: html_document
self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages required to run the analysis and the plotting.

```{r}
library('lattice')
library('graphics')
library('psyphy')
library('MASS')
library('glm2')
library('readr')
```

## Reading in the data

The script is constructed such that you should have one column with the number of correct choices ("corr" in the current version), second column with the number of incorrect choices("incorr" in the current version), and a third column representing the stimulus levels ("lint" in the current version; could be intensity, or whatever). Additional variables can be added.

```{r}
orange.df <- read_delim('orange_colours.txt', delim="\t") 
orange.df$background <- factor(orange.df$background)
orange.df$ind <- factor(orange.df$ind)
orange.df$batch <- as.factor(orange.df$batch)
```

## Model testing, full and removing one factor at a time

### setting up models

Null model, data is explained only by variance. lambda.init is your estimate of the upper asymptote and NumAlt specifies the number of alternatives e.g. 2 alternative forced choice.


Orange colours

Model testing, null model and full model, and models removing one factor
```{r}
orange.mod.0 <- glm.WH(cbind(corr,incorr)~1, data = orange.df, lambda.init = 0.1, interval = c(0, 1), NumAlt = 2) # Null model, data is explained only by variance. lambda.init is your estimate of the upper asymptote and NumAlt specifies the number of alternatives e.g. 2 alternative forced choice
```
full model with 3-way interaction
```{r}
orange.mod.1 <- glm.WH(cbind(corr,incorr)~Colour.difference*background*sex+ind+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```

after removing 3-way interaction
```{r}
orange.mod.2 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+Colour.difference*sex+background*sex+ind+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

removing interaction
```{r}
orange.mod.31 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+sex+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```

removing sex
```{r}
orange.mod.4 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```

removing ind
```{r}
orange.mod.41 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+sex, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```

removing sex and ind
```{r}
orange.mod.51 <- glm.WH(cbind(corr,incorr)~Colour.difference*background, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=1000) # Model where data is affected by the stimulus level
```

```{r}
orange.mod.21 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+Colour.difference*sex+background*sex+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```


```{r}
orange.mod.22 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+Colour.difference*sex+background*sex+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```


Compare all
```{r}
anova(orange.mod.1,orange.mod.2,test="Chisq")
anova(orange.mod.1,orange.mod.21,test="Chisq")
anova(orange.mod.1,orange.mod.22, test="Chisq")
```

Model comparison
```{r}
AIC(orange.mod.0,orange.mod.1,orange.mod.2, orange.mod.21, orange.mod.22)
```

removing batch
```{r}
orange.mod.3 <- glm.WH(cbind(corr,incorr)~Colour.difference*background*sex+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

removing individual identity
```{r}
orange.mod.4 <- glm.WH(cbind(corr,incorr)~Colour.difference*background*sex+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

removing batch and ind
```{r}
orange.mod.5 <- glm.WH(cbind(corr,incorr)~Colour.difference*background*sex, data = orange.df, lambda.init = 0.1, interval = c(0, 1), NumAlt = 2, maxit=100) # Model where data is affected by the stimulus level
```

Model comparison
```{r}
anova(orange.mod.1,orange.mod.3,test="Chisq")
anova(orange.mod.1,orange.mod.4,test="Chisq")
anova(orange.mod.1,orange.mod.5,test="Chisq")

AIC(orange.mod.0, orange.mod.1, orange.mod.2, orange.mod.3, orange.mod.4, orange.mod.5)
```

Compare all
```{r}
anova(orange.mod.0,orange.mod.1,test="Chisq")
anova(orange.mod.1,orange.mod.2,test="Chisq")
anova(orange.mod.1,orange.mod.3,test="Chisq")
anova(orange.mod.1,orange.mod.4,test="Chisq")
anova(orange.mod.1,orange.mod.5,test="Chisq")


summary(orange.mod.1)
```


```{r}
orange.mod.3 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+batch+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2) # Model where data is affected by the stimulus level
```


```{r}
orange.mod.4 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+sex+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2) # Model where data is affected by the stimulus level
```


```{r}
orange.mod.5 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+batch+sex+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2) # Model where data is affected by the stimulus level
```

Compare model 1 with null model
```{r}
anova(orange.mod.0,orange.mod.1,test="LRT")
```

Compare models 1 & 2
```{r}
anova(orange.mod.1,orange.mod.2,test="LRT")
```

Compare model 1 & model 3
```{r}
anova(orange.mod.1,orange.mod.3,test="LRT")
```

Compare model 1 & model 4
```{r}
anova(orange.mod.1,orange.mod.4,test="Chisq")
```

Compare model 1 & model 5
```{r}
anova(orange.mod.1,orange.mod.5,test="Chisq")
```

*no model with a reduction in a single variable reduces deviance,*
*thus the full model should be preferred.*

#Alternate interpretation
######## *However, performed as below, orange.mod.3 is preferred* ###########
```{r}
anova(orange.mod.1,orange.mod.2,orange.mod.3,orange.mod.4,orange.mod.5, test="Chisq")
```

```{r}
orange.mod.3 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+batch+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2) # Model where data is affected by the stimulus level
```

```{r}
orange.mod.31 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+batch, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2) # Model where data is affected by the stimulus level
```

```{r}
orange.mod.32 <- glm.WH(cbind(corr,incorr)~Colour.difference*background+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2) # Model where data is affected by the stimulus level
```

```{r}
orange.mod.33 <- glm.WH(cbind(corr,incorr)~Colour.difference+background+batch+ind, data = orange.df, lambda.init = 0.05, interval = c(0, 1), NumAlt = 2) # Model where data is affected by the stimulus level
```

Model comparison
```{r}
anova(orange.mod.3,orange.mod.31,orange.mod.32,orange.mod.33, test="Chisq")
```